Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-12 src/tex/ms.tex
explain why these HZ limits

The \gls{HZ} describes a region around a star where a planet with Earth's atmospheric composition and climate feedbacks can maintain liquid water on its surface~\citep[e.g.,][]{Ramirez2017,Ramirez2018,MolLous2022,Spinelli2023,Tuchow2023}.
Here, we adopted orbital distance estimates that define the \gls{HZ} as the region between the runaway greenhouse transition, where the stellar instellation cannot anymore be balanced through infrared cooling to space~\citep{Ingersoll1969}, and the maximum greenhouse limit, corresponding to the maximum distance at which surface temperatures allowing liquid water can be maintained through a CO$_2$ greenhouse effect~\citep{Kasting1991,Kasting1993,Underwood2003,Kopparapu2013,Kopparapu2014}.
We used the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent distance limits of the \gls{HZ} $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
\rev{The specific boundaries of the habitable zone are known to be sensitive to the star’s luminosity, spectral type, the planet’s mass, and the planet’s atmospheric properties~\citep[e.g.,][]{Pierrehumbert2011,Ramirez2014,Ramirez2017,Ramirez2018b,Koll2019,Ramirez2018,Ramirez2020,Bonati2021,Chaverot2022,Turbet2023}.
The specific habitable zone limits can therefore be variable.
Here -- to constrain the complexity of this study -- we adopted a conservative approach that uses the commonly used limits.
}

>>>>

The \gls{HZ} describes a region around a star where a planet with Earth's atmospheric composition and climate feedbacks can maintain liquid water on its surface~\citep[e.g.,][]{Ramirez2017,Ramirez2018,MolLous2022,Spinelli2023,Tuchow2023}.
Here, we adopted orbital distance estimates that define the \gls{HZ} as the region between the runaway greenhouse transition, where the stellar instellation cannot anymore be balanced through infrared cooling to space~\citep{Ingersoll1969}, and the maximum greenhouse limit, corresponding to the maximum distance at which surface temperatures allowing liquid water can be maintained through a CO$_2$ greenhouse effect~\citep{Kasting1991,Kasting1993,Underwood2003,Kopparapu2013,Kopparapu2014}.
\rev{The exact boundaries of the habitable zone are known to be sensitive to the star’s luminosity, spectral type, the planet’s mass, and the planet’s atmospheric properties~\citep[e.g.,][]{Pierrehumbert2011,Ramirez2014,Ramirez2017,Ramirez2018b,Koll2019,Ramirez2018,Ramirez2020,Bonati2021,Chaverot2022,Turbet2023}.
Here, we adopted the commonly used parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent distance limits of the \gls{HZ} $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
}
